---
title: "Introduction to ggplot2"
author: "Samruddhi Somani"
date: "March 1, 2017"
output:
  revealjs::revealjs_presentation:
    self_contained: false
    center: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,messages=FALSE)
```

Setup  
---
```{r,results="hide",message=FALSE,warning=FALSE}
#installation
# install.packages(c("ggplot2","ggthemes","ggforce","cowplot"),
#                 dependencies=TRUE,
#                 repos="http://cran.revolutionanalytics.com/")

#loading
library(ggplot2) #grammar of graphics
library(ggthemes) #optional: switch to popular themes
library(cowplot) #optional: layouts
```
---

```{r}
sessionInfo()
```

ggplot2 Philosophy
---
"grammar of graphics, the idea that you can build every graph from the same components: a data set, a coordinate system, and geoms--visual marks that represent data points" 

~ RStudio

Data Details  
---
```{r}
head(diamonds)
```
---

Introduction to Geoms
---
```{r,fig.height=3, fig.width=15}
baseg=ggplot(diamonds, aes(x=cut,y=price))+
    theme_few()+
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

g_point=baseg+geom_point()+ggtitle("Point")
g_jitter=baseg+geom_jitter(alpha=.3)+ggtitle("Jitter")
g_box=baseg+geom_boxplot()+ggtitle("Box")
g_violin=baseg+geom_violin()+ggtitle("Violin")


plot_grid(g_point,g_jitter,g_box,g_violin,ncol=4) #display
```

Overlaying Geoms
---

```{r,fig.height=3,fig.width=15, message=FALSE,warning=FALSE}
base_layer=ggplot(diamonds,aes(x=carat,y=price))+
    theme(legend.position=c(.9,.3))+
    guides(color=guide_legend(nrow=3,byrow=TRUE))

g_point=base_layer+geom_point(alpha=.1)+ggtitle("Point")
g_line=g_point+geom_smooth(color='red')+ggtitle("Line")
g_colors=base_layer+geom_point(alpha=.3,aes(color=cut))+ggtitle('Colors')
g_groups=g_colors+geom_smooth(aes(color=cut))+ggtitle("Groups")
plot_grid(g_point,g_line,g_colors,g_groups,ncol=4)
```

Faceting: Small Multiples
---

```{r,fig.height=3,fig.width=12,message=FALSE}
base_layer+geom_point()+geom_smooth()+facet_grid(.~cut)
```
---
  
Resources
---
- ggplot2 documentation
- R Graphics Cookbook
- StackOverflow
- Rstudio Cheat Sheet